FAO bivalve production

### 2021-08-12 analysis/SI_figs.Rmd
cleaned up scripts and READMEs

```{r}
all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")

@@

if(is.empty(count_green) == TRUE){
    count_green = 0
  }

@@

if(is.empty(count_yellow) == TRUE){
    count_yellow = 0
  }

@@

if(is.empty(count_red) == TRUE){
    count_red = 0
  }

>>>>

```{r}
all_farms_sf <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

@@

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv")

@@

if(is_empty(count_green) == TRUE){
    count_green = 0
  }

@@

if(is_empty(count_yellow) == TRUE){
    count_yellow = 0
  }

@@

if(is_empty(count_red) == TRUE){
    count_red = 0
  }

### 2021-08-12 analysis/match_data_sources.Rmd
cleaned up scripts and READMEs

This script takes the farms dataset produced from prior steps, and matches to our data source spreadsheet, so that each point in the final database has a source associated with it (or an NA, if it was estimated).

@@

all_farms <- readRDS("data/all_modeled_marine_farms_31km.rds") %>%
  left_join(all_farms_to_place) %>%
    mutate(data_type = case_when(
    source == "real" ~ "known locations", 
    source == "modeled" & estimated == 0 ~ "modeled locations, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled locations, estimated number of farms"
  )) %>%
  mutate(estimated = ifelse(is.na(estimated), 0, estimated))

@@

## data types D, and E recieve global prod per farm estimates.

@@

## USA Bivalve fix: 
USA_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "USA", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known location") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = ifelse(NAME_1 == "Washington"| NAME_1 == "Rhode Island", ds_2, ds_1)) %>% 
  mutate(data_year = 2018) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

## AUS Bivalve fix: 
AUS_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "AUS", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known location") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = ifelse(NAME_1 == "Victoria", ds_1, ds_2)) %>%
  mutate(data_year = 2021) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

## rows 1-40 are lee, rows 41-66 are kuo
TWN_finfish_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "TWN", 
               species == "General Marine Fish", 
               data_type == "known location") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>% 
  separate(col = data_year, into = c("dy_1", "dy_2"), sep = ",") %>% 
  mutate(row = row_number()) %>%
  mutate(data_source = ifelse(row %in% c(1:40), ds_1, ds_2)) %>%
  mutate(data_year = ifelse(row %in% c(1:40), dy_1, dy_2)) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

all_farms_sources_final <- all_farms_sources %>%
  filter(iso3c != "CAN"|species != "Salmonids") %>%
  filter(iso3c != "CAN"|species != "Unfed or algae fed shellfish") %>%
  filter(iso3c != "USA"|species != "Salmonids") %>%
  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known location") %>%
  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known location") %>%
  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known location") %>%
  filter(iso3c != "USA"|species != "Shrimp") %>%
  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix) %>%
  mutate(data_year = as.numeric(data_year)) %>%
  dplyr::select(-species)

@@

## Now save this as a csv
st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources_31km.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")

test <- all_farms %>%
  filter(iso3c == "IND", str_detect(species_group, "bivalve"))
```

>>>>

This script takes the farms dataset produced from prior steps, and matches to our data source spreadsheet (created manually in our literature review), so that each point in the final database has a source associated with it (or an NA, if it was estimated).

@@

all_farms <- readRDS("data/all_modeled_marine_farms_final.rds") %>%
  left_join(all_farms_to_place) %>%
    mutate(data_type = case_when(
    source == "real" ~ "known locations", 
    source == "modeled" & estimated == 0 ~ "modeled locations, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled locations, estimated number of farms"
  )) %>%
  mutate(estimated = ifelse(is.na(estimated), 0, estimated))

@@

## data types D, E, and F receive global prod per farm estimates.

@@

## USA Bivalve fix: 
USA_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "USA", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known locations") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = ifelse(NAME_1 == "Washington"| NAME_1 == "Rhode Island", ds_2, ds_1)) %>% 
  mutate(data_year = 2018) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

## AUS Bivalve fix: 
AUS_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "AUS", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known locations") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = ifelse(NAME_1 == "Victoria", ds_1, ds_2)) %>%
  mutate(data_year = 2021) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

## rows 1-40 are lee, rows 41-66 are kuo
TWN_finfish_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "TWN", 
               species == "General Marine Fish", 
               data_type == "known locations") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>% 
  separate(col = data_year, into = c("dy_1", "dy_2"), sep = ",") %>% 
  mutate(row = row_number()) %>%
  mutate(data_source = ifelse(row %in% c(1:40), ds_1, ds_2)) %>%
  mutate(data_year = ifelse(row %in% c(1:40), dy_1, dy_2)) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

all_farms_sources_final <- all_farms_sources %>%
  filter(iso3c != "CAN"|species != "Salmonids") %>%
  filter(iso3c != "CAN"|species != "Unfed or algae fed shellfish") %>%
  filter(iso3c != "USA"|species != "Salmonids") %>%
  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known locations") %>%
  filter(iso3c != "USA"|species != "Shrimp") %>%
  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix) %>%
  mutate(data_year = as.numeric(data_year)) %>%
  dplyr::select(-species)

@@

## Now save this as a csv
st_write(all_farms_sources_final, "data/all_marine_aquaculture_farms_sources_final.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)

@@

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv")

test <- all_farms %>%
  filter(iso3c == "CRI", str_detect(species_group, "hrimp")) %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

mapview(test)

### 2021-08-12 analysis/paper_figs.Rmd
cleaned up scripts and READMEs

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(RCurl)
library("rnaturalearth")
library("rnaturalearthdata")
library(cowplot) 
library(ggpubr)
library(RColorBrewer)
library(OpenStreetMap)
library(ggspatial)
library(ggplot2)
library(patchwork)

@@

test <- all_farms_sf %>%
  filter(iso3c == "HRV")
mapview(test) ## one weird MFG from ASC

test <- all_farms_sf %>%
  filter(iso3c == "TUR")
mapview(test) ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
  mutate(data_type_plot = case_when(
    data_type == "modeled locations, known number of farms" ~ "Modeled locations, known number of farms",
    data_type == "modeled locations, estimated number of farms" ~ "Modeled locations, estimated number of farms", 
    data_type == "known locations" ~ "Known locations"
  ))

@@

chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
  theme(legend.position = "bottom", ## put legend on bottom
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("A")  # + 
 #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
chl_zoom

## China - near 
chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.key = element_rect(fill = NA),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("D")
chn_zoom

## Ecuador - Near Guayaquil
ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("B")
ecu_zoom

@@

## USA NE 
usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C")

@@

## Plot with USA instead of norway

@@

>>>>

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(RCurl)
library("rnaturalearth")
library("rnaturalearthdata")
library(cowplot) 
library(ggpubr)
library(RColorBrewer)
library(OpenStreetMap)
library(ggspatial)
library(ggplot2)
library(patchwork)
library(rfishbase)

@@

test <- all_farms_sf %>%
  filter(iso3c == "HRV")
mapview(test, zcol = "data_type") ## one weird MFG from ASC

test <- all_farms_sf %>%
  filter(iso3c == "ECU")
mapview(test, zcol = "data_type") ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...

test <- all_farms_sf %>%
  filter(data_type_2 %in% c("A", "B", "C"))
sum(test$tonnes_per_farm)

3568135/sum(all_farms_sf$tonnes_per_farm) # 0.1203892

4963244/sum(all_farms_sf$tonnes_per_farm) # 0.1674603

@@

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>% 
  mutate(data_type_plot = case_when(
    data_type == "modeled locations, known number of farms" ~ "Modeled locations, known number of farms",
    data_type == "modeled locations, estimated number of farms" ~ "Modeled locations, estimated number of farms", 
    data_type == "known locations" ~ "Known locations"
  ))

@@

chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1.25, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
  theme(legend.position = "bottom", ## put legend on bottom
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("A")  # + 
 #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
chl_zoom

## China - near 
chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1.3, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.key = element_rect(fill = NA),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("D")
chn_zoom

## Ecuador - Near Guayaquil
ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1.3, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("B")
ecu_zoom

@@

## USA NE 
usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C") # + 
 # scale_alpha_manual(values = c(0.7, 0.7, 1))

@@

## Chile and Ecuador

@@

## USA and China

### 2021-08-12 analysis/paper_stats.Rmd
cleaned up scripts and READMEs

>>>>

sum(all_farms$tonnes_per_farm) # 29638328

data_type_A <- all_farms %>%
  filter(data_type_2 == "A")

sum(data_type_A$tonnes_per_farm) # 3568135

data_type_no_A <- all_farms %>%
  filter(data_type_2 != "A")
sum(data_type_no_A$tonnes_per_farm) # 26070193

26070193/29638328 # 0.8796108

test <- all_farms %>%
  filter(species_group == "General marine fish")

sum(test$tonnes_per_farm) # 3909255

3909255/29638328 # 0.1318986

### 2021-08-12 analysis/validation_testing.Rmd
cleaned up scripts and READMEs

## food 81km2 at equator 
eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask.tif"))
plot(area(eez_81))

@@

```{r}
validation_all <- readRDS(file.path("data/all_validation_farms.rds"))  %>%
  mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
                          type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
                          type == "shrimp" ~ "Shrimps and prawns", 
                          type == "tuna" ~ "Bluefin tuna", 
                          type == "marine_fish_general" ~ "General marine fish"))

@@

 - AUC of ~0.61
```{r}

@@

sum(eez_cells_df$predicted, na.rm = TRUE) # 8446

@@

cellStats(test,"sum") 
# layer.1 layer.2 
#    8455    7917

@@

 - AUC of ~0.59 - worse than 36km2... makes sense! 
```{r}

@@

sum(eez_cells_df$predicted, na.rm = TRUE) # 8450

@@

cellStats(test,"sum") 
# layer.1 layer.2 
#    8450    8386

@@

 - AUC of ~0.7241861 ; makes sense that is it better!

@@

@@

@@

Resampling test: 
```{r}

### Manual equal rebalancing
z_ind <- which(eez_cells_df$pred_count == 1)
zz_ind <- which(eez_cells_df$pred_count == 0)

nsamp = 3455
pick_z <- sample(z_ind, nsamp)
pick_zz <- sample(zz_ind, nsamp)

new_data <- eez_cells_df[c(pick_z, pick_zz), ]

confusion_mat <- caret::confusionMatrix(data = as.factor(new_data$pred_count), reference = as.factor(new_data$real_count))

pred = new_data$pred_count

pred = prediction(pred, new_data$real_count)

auc = performance(pred, measure = "auc")
print(auc@y.values)
# 0.7264348

#### Over/undersampling 
install.packages("ROSE")
library(ROSE)

test <- eez_cells_df %>%
  filter(pred_count == 1)

## not sure what the statistically correct way of picking the sampling number is... 
data_balanced_under <- ovun.sample(pred_count ~ real_count, data = eez_cells_df, method = "under", N = 8455)
table(data_balanced_under$data)

#           real_count
# pred_count    0    1
#          0 4894  106
#          1 2761  694

## still pretty unbalanced, but it is a lot better than it was...

recall <- 694/(694+106) # 0.8675

precision <- 694 / (694 + 2761) # 0.20

accuracy <- (4894 + 2761)/(4894 + 2761 + 106 + 694) # 0.91

sensitivity = (4894)/(4894 + 2761) # 0.64

balanced_accuracy <- (recall + sensitivity)/2 # 0.75 - this is also the AUC - which is pretty good.

g_measure <- sqrt(precision*recall) # 0.42

false_pos_rate <- 2761/(2761+4894) # 0.36

>>>>

## food 81km2 at equator 
eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask.tif"))
plot(raster::area(eez_81))

cellStats(raster::area(eez_81), "mean")

test <- data.frame(raster::values(raster::area(eez_81)))

@@

```{r}
validation_all <- readRDS(file.path("data/all_validation_farms_fix_shrimp.rds"))  %>%
  mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
                          type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
                          type == "shrimp" ~ "Shrimps and prawns", 
                          type == "tuna" ~ "Bluefin tuna", 
                          type == "marine_fish_general" ~ "General marine fish"))

@@

 - AUC of ~0.60
```{r}

@@

sum(eez_cells_df$predicted, na.rm = TRUE) # 8442

@@

cellStats(test,"sum") 
# layer.1 layer.2 
#    8442    8377

@@

 - AUC of ~0.58 - worse than 36km2... makes sense! 
```{r}

@@

sum(eez_cells_df$predicted, na.rm = TRUE) # 8445

@@

cellStats(test,"sum") 
# layer.1 layer.2 
#    8445    8386

@@

 - AUC of ~7042 ; makes sense that is it better!

@@

plot(val_rast, col = "black")

@@

## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra farms.

@@

### 2021-08-12 marine/STEP1_species_groups/STEP1_species_groups.Rmd
cleaned up scripts and READMEs

---
title: "Exploring FAO aquaculture data"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

@@

## explore marine
```{r}

@@

Classify species into aquaculture groups 
```{r}
# Need to classify into these groups, for easier mapping and pressure calculations: 
#  - Bivalves
#  - Tuna
#  - Salmonids
#  - Shrimps and Prawns
#  - crustaceans
#  - marine fish general (all the other finfish species)

@@

fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017,
                !is.na(value),
                !is.na(aq_group)) %>%
   dplyr::filter(value >= 500) %>%
  group_by(aq_group, country, species, year) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup() # %>%
  # dplyr::filter(tonnes >= 500) %>%
 #  group_by(country, year) %>%
 #  summarise(total_tonnes = sum(tonnes))# %>%
 # # arrange(aq_group)

@@

## Take a look at the data 
test <- fao_1 %>%
  dplyr::filter(aq_group == "bivalves")
sum(test$tonnes) # 17435623

@@

test <- fao_1 %>%
  dplyr::filter(aq_group == "crustaceans")
sum(test$total_tonnes) # 5094133

test <- fao_1 %>%
  dplyr::filter(aq_group == "marine_fish_general")
sum(test$total_tonnes) # 5094133

test <- fao_1 %>%
  dplyr::filter(aq_group == "tuna")
sum(test$total_tonnes) # 5094133

test <- fao_1 %>%
  dplyr::filter(aq_group == "salmonids")
sum(test$total_tonnes) # 5094133

>>>>

---
title: "Prepping FAO aquaculture data"
author: "Gage Clawson (USCB, NCEAS, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script preps and classifies the FAO aquaculture data to the appropriate production types and species.

@@

Read in the raw FAO data
```{r}

@@

## Prep marine and brackish-water
```{r}

@@

Classify species into mariculture groups consistent with MacLeod et al. 2020 (https://www.nature.com/articles/s41598-020-68231-8)

Need to classify into these groups, for easier mapping and pressure calculations:
 - Bivalves (Unfed or algae fed bivalve molluscs)
 - Tuna (Bluefin tuna)
 - Salmonids (Salmonidae fish)
 - Shrimps and Prawns
 - crustaceans (Non-shrimp crustaceans)
 - marine fish general (General marine fish)

@@

fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017,
                !is.na(value),
                !is.na(aq_group)) %>%
   dplyr::filter(value >= 500) %>%
  group_by(aq_group, country, species, year) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup()

@@

Explore the data

```{r}
## Take a look at the data 
test <- fao_1 %>%
  dplyr::filter(aq_group == "bivalves")
sum(test$tonnes) # 17435623

@@

test <- fao_1 %>%
  dplyr::filter(aq_group == "crustaceans")
sum(test$total_tonnes) #

test <- fao_1 %>%
  dplyr::filter(aq_group == "marine_fish_general")
sum(test$total_tonnes) #

test <- fao_1 %>%
  dplyr::filter(aq_group == "tuna")
sum(test$total_tonnes) #

test <- fao_1 %>%
  dplyr::filter(aq_group == "salmonids")
sum(test$total_tonnes) #

### 2021-08-12 marine/STEP1_species_groups/STEP2_ASC_data_prep.Rmd
cleaned up scripts and READMEs

---
title: "Prep ASC data"
output: html_document
---

@@

See how many countries from FAO are represented in ASC for marine_fish_general category

```{r}
fao_marine_fish <- fao_all %>%
  dplyr::filter(aq_group == "marine_fish_general")

ASC_marine_fish <- ASC_all_sf %>%
  dplyr::filter(aq_group == "marine_fish_general")

setdiff(fao_marine_fish$country, ASC_marine_fish$cert_country)

#  [1] "Bangladesh"               "Cambodia"                 "China"                   
#  [4] "China, Hong Kong SAR"     "Costa Rica"               "Cyprus"                  
#  [7] "Egypt"                    "France"                   "India"                   
# [10] "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [13] "Italy"                    "Korea, Republic of"       "Malaysia"                
# [16] "Malta"                    "Mauritius"                "Norway"                  
# [19] "Philippines"              "Portugal"                 "Saudi Arabia"            
# [22] "Singapore"                "Taiwan Province of China" "Tunisia"                 
# [25] "United Arab Emirates"

setdiff(ASC_marine_fish$cert_country, fao_marine_fish$country)
# [1] "Netherlands" "Denmark"     "Germany"

unique(ASC_marine_fish$cert_country)
```

See how many countries from FAO are represented in ASC for bivalves category

```{r}
fao_bivalve <- fao_all %>%
  dplyr::filter(aq_group == "bivalves")

ASC_bivalve <- ASC_all_sf %>%
  dplyr::filter(aq_group == "bivalves")

setdiff(fao_bivalve$country, ASC_bivalve$cert_country)

#  [1] "Brazil"                   "Bulgaria"                 "Cambodia"                
#  [4] "Canada"                   "China, Hong Kong SAR"     "Croatia"                 
#  [7] "Cuba"                     "Denmark"                  "French Polynesia"        
# [10] "Germany"                  "Greece"                   "Guernsey"                
# [13] "India"                    "Indonesia"                "Ireland"                 
# [16] "Italy"                    "Jersey"                   "Korea, Dem. People's Rep"
# [19] "Malaysia"                 "Netherlands"              "Norway"                  
# [22] "Philippines"              "Russian Federation"       "Slovenia"                
# [25] "Spain"                    "Sweden"                   "Taiwan Province of China"
# [28] "Thailand"                        "United States of America"

setdiff(ASC_bivalve$cert_country, fao_bivalve$country)
# United kingdom spelled differently.. don't worry about it

unique(ASC_bivalve$cert_country)
```

Tuna
```{r}
fao_tuna <- fao_all %>%
  dplyr::filter(aq_group == "tuna")

ASC_tuna <- ASC_all_sf %>%
  dplyr::filter(aq_group == "tuna")

unique(fao_tuna$country)
```

Crustaceans
```{r}
fao_crust <- fao_all %>%
  dplyr::filter(aq_group == "crustaceans")

ASC_crust <- ASC_all_sf %>%
  dplyr::filter(aq_group == "crustaceans")

unique(fao_crust$country)
```

>>>>

---
title: "Prep ASC data"
author: "Gage Clawson (USCB, NCEAS, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

### 2021-08-12 marine/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
cleaned up scripts and READMEs

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

@@

## write out bivalve taxa and production for Juliette
fao_bivalve_taxa_prod <- fao %>%
  filter(species %in% bivalve_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

@@

Abalones nei, American cupped oyster, Aquatic invertebrates nei, Australian mussel, Blacklip pearl oyster, Blood cockle, Blue mussel, Butter clam, Chilean mussel, Cholga mussel, Choro mussel, Clams, etc. nei, Common edible cockle, Constricted tagelus, Cortez oyster, Cupped oysters nei, European flat oyster, Flat and cupped oysters nei, Green mussel, Grooved carpet shell, Indian backwater oyster, Inflated ark, Japanese carpet shell, Japanese hard clam, Japanese sea cucumber, Korean mussel, Mangrove cupped oyster, Marine molluscs nei, Mediterranean mussel, New Zealand mussel, Northern quahog, Pacific cupped oyster, Pacific geoduck, Pen shells nei, Penguin wing oyster, Perlemoen abalone, Peruvian calico scallop, Red abalone, Sand gaper, Scallops nei, Sea cucumbers nei, Sea mussels nei, Sea snails, Sea squirts nei, Sea urchins nei, Slipper cupped oyster, South American rock mussel, Yesso scallop

>>>>

## Read in fao data and get a species list for bivalve 
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

@@

## write out bivalve taxa and production
fao_bivalve_taxa_prod <- fao %>%
  filter(species %in% bivalve_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  # group_by(country, year) %>%
  # summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

sum(fao_bivalve_taxa_prod$fao_tonnes_production) # 17435623
unique(fao_bivalve_taxa_prod$country) # 42 countries

@@

Species included: 
Abalones nei, American cupped oyster, Aquatic invertebrates nei, Australian mussel, Blacklip pearl oyster, Blood cockle, Blue mussel, Butter clam, Chilean mussel, Cholga mussel, Choro mussel, Clams, etc. nei, Common edible cockle, Constricted tagelus, Cortez oyster, Cupped oysters nei, European flat oyster, Flat and cupped oysters nei, Green mussel, Grooved carpet shell, Indian backwater oyster, Inflated ark, Japanese carpet shell, Japanese hard clam, Japanese sea cucumber, Korean mussel, Mangrove cupped oyster, Marine molluscs nei, Mediterranean mussel, New Zealand mussel, Northern quahog, Pacific cupped oyster, Pacific geoduck, Pen shells nei, Penguin wing oyster, Perlemoen abalone, Peruvian calico scallop, Red abalone, Sand gaper, Scallops nei, Sea cucumbers nei, Sea mussels nei, Sea snails, Sea squirts nei, Sea urchins nei, Slipper cupped oyster, South American rock mussel, Yesso scallop
